\textsf{Are frontier models superhuman chemists?}

### 2024-03-11 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\subparagraph{Periodic table}
The questions are framed based on the reference periodic table from the Royal Society of Chemistry (\url{https://www.rsc.org/periodic-table/}), covering various aspects and trends of the periodic table.

>>>>

\subparagraph{Periodic table}
The questions are manually created based on the reference periodic table from the Royal Society of Chemistry (\url{https://www.rsc.org/periodic-table/}), covering various aspects and trends of the periodic table.
